Exploring mathematical objects from custom-tailored mathematical universes

### 2020-06-30 paper-filmat.tex
Clearer definition (in response to review)

\begin{defn}A \emph{topos} (more precisely \emph{elementary topos} or
\emph{logos} with a natural numbers object) is a category which has all finite
limits, is cartesian closed, has a subobject classifier and contains a natural
numbers object.\end{defn}

>>>>

\begin{defn}A \emph{topos} is a category which has all finite
limits, is cartesian closed, has a subobject classifier and contains a natural
numbers object.\footnote{More precisely, this is the definition of an
\emph{elementary topos with a natural numbers object}. Since this definition is
less tied to geometry than Grothendieck's (as categories of sheaves over
sites), there is a trend to call these toposes \emph{logoses}. However, that
term also has other uses.}\end{defn}
